A Closer Look at Network Flow on Evolving Graphs

### 2018-05-14 paper.tex
add pagerank example

For evolving graphs, we replace out-neighbours with forward neighbours which preserve the direction of time.
Then the Katz score of a node $i$ at time stamp $t$, denoted by $(i,t)$, is the sum of influence of all the active nodes that $(i,t)$ can reach via a time-preserving walk.
Unlike \cite{grindrod11}, we also consider the temporal distance between two nodes. For example, the temporal distance between $(i, 2001)$ and $(i, 2018)$ is $17$.
% julia code implementation
With the defintion of \texttt{temporal\_distance} introduced in Section \ref{sec:time-pres-paths}.
We define the temporal Katz score of node $(i, t)$ as

\begin{lstlisting}
function temporal_katz(g::AbstractEvolvingGraph,
  v::TimeNode; alpha = 0.1, max_level = 5)
  score = 0.
  fronter = [v]
  level = 0
  while level < max_level
      next = []
      for u in fronter
          for v in forward_neighbors(g, u)
              push!(next, v)
              d = temporal_distance(v, u)
              d += level
              score += alpha^d
          end
      end
      fronter = next
      level += 1
  end
  return score
end
\end{lstlisting}

% explain the code
The algorithm \texttt{temporal\_katz} performs breadth first search (BFS) starting at \texttt{TimeNode} $v$, which represent a node at a specific time stamp \footnote{See also \url{https://etymoio.github.io/EvolvingGraphs.jl/latest/base.html#EvolvingGraphs.TimeNode}}.
For each \texttt{TimeNode} $v$, we accumulate the influence of linked nodes according to their spatial and temporal
distance from $v$. The spatial distance is recorded in variable \texttt{level} and the temporal distance is calculated by
\texttt{temporal\_distance}.

% example on 3 timestamp evolving graph

@@

Let $A$ be an adjacency

In \cite{grindrod11}, Grindrod et al. define a \emph{dynamic walk} of length $m$ from
node $v_1$ to node $v_{w+1}$  as a sequence of edges
$(v_1, v_2), (v_2, v_3), \ldots (v_w, v_{w+1})$ and a non-decreasing sequence of times
$t_{r_1} \leq t_{r_2} \leq \cdots \leq t_{r_w}$ such that the adjacency matrix at time stamp
$r_m$, i.e., $A_{i_m, i_{m+1}}^{[r_m]} \ne 0$. Note that in this definition the authors only take account of the static edges and the length of a dynamic walk is determined by the number of static edges.

The Katz centrality is based on a sequence of matrix products
\begin{equation}
\label{eq:katz}
Q = (I - \alpha A^{[0]})^{-1}(I - \alpha A^{[1]})^{-1} \cdots (I - \alpha A^{[M]})^{-1}.
\end{equation}
The $i$th row and column sums
$$
C_i^{broadcast} = \sum_{k=1}^n Q_{ik}, \quad C_i^{receive} = \sum_{k=1}^n Q_{ki}
$$
are the broadcast centrality and receive centrality of node $i$.

Note that the $(i,j)$th element of adjacency matrix $A^k$ counts the only of paths from $i$ to $j$.
To simulate a Katz centrality,
the shortest path algorithms search through all possible paths between $i$ and $j$.

>>>>

For evolving graphs, we replace out-neighbours with forward neighbours which preserve the direction of time.
Then the Katz score of a node $i$ at time stamp $t$, denoted by $(i,t)$, is the sum of influence of all the active nodes that $(i,t)$ can reach via a time-preserving walk.
Unlike \cite{grindrod11}, we also consider the temporal distance between two nodes. For example, the temporal distance between $(i, 2001)$ and $(i, 2018)$ is $17$.
% julia code implementation
With the definition of \texttt{temporal\_distance} introduced in Section \ref{sec:time-pres-paths}.
We define the temporal Katz score of node $(i, t)$ as

\begin{lstlisting}
function temporal_katz(g::AbstractEvolvingGraph,
  start::TimeNode; alpha = 0.1, max_level = 5)
    score = 0.
    v = start
    fronter = [v]
    level = 0
    while level < max_level
        next = []
        for u in fronter
            for v in forward_neighbors(g, u)
                push!(next, v)
                td = temporal_distance(start, u)
                d = td + level
                score += alpha^d
            end
        end
        fronter = next
        level += 1
    end
    return score
end
\end{lstlisting}

% explain the code
The algorithm \texttt{temporal\_katz} performs breadth first search (BFS) starting at \texttt{TimeNode} $v$, which represent a node at a specific time stamp \footnote{See also \url{https://etymoio.github.io/EvolvingGraphs.jl/latest/base.html#EvolvingGraphs.TimeNode}}.
For each \texttt{TimeNode} $v$, we accumulate the influence of linked nodes according to their spatial and temporal
distance from $v$. The spatial distance is recorded in variable \texttt{level} and the temporal distance is calculated by
\texttt{temporal\_distance}. The algorithm stops searching when \texttt{level} is larger or equal to \texttt{max\_level}.

% example on 3 timestamp evolving graph
For Figure \ref{}

@@
